Mapping plant-pollinator interactions across Europe

### 2024-02-09 Manuscript/Ms.qmd
Paragraph 2 outline

1st paragraph

General introduction of how global change impacts plant-pollinator interactions

Maybe expand on some drivers? Climate change, habitat fragmentation, agricultural intensification, urbanization, pollution, pesticides and species' invasions

Highlight the relevance of large scale datasets to understand biological phenomena

2nd paragraph

@@

>>>>

The interaction between plants and pollinators is one of the most well-documented mutualisms on Earth. Plant-pollinator interactions involve a great diversity of species, largely attributed to their coevolutive history [@ollerton2017], and are critically important for terrestrial biodiversity and the human economy. The synergistic effects of climate change with other global change pressures are threatening worldwide biodiversity [@sala2000; @bellard2014], including plant and pollinator species as well as their interactions [@gonzalez2013; @settele2016]. Under this scenario, the increasing availability of biodiversity data plays a major role in our ecological understanding of species and guiding conservation planning. However, our knowledge of plant and pollinator species and their network of interactions still exhibits major temporal, spatial and taxonomic biases [@archer2014; @troia2016;  @poisot2021] that limit our ability to effectively protect their biodiversity.

Integrating ecological data is allowing researchers to understand biological patterns [REF]. Europe is one of the continents with larger information of plant and pollinator biodiversity data available that is proven by the different checklists of species of plants [ref], bees [ref], syrphids [REF] or butterflies [REF]. However,

SOMETHING ABOUT THE DIFFICULTY OF CAPTURING ECOLOGICAL INTERACTIONS
Jordano Funct Ecol?

connectance/ecological networks

what we know-->Plant-pollinator databases? -->Mangal/Web of life/the new one that has a bit of everything...

Maybe add another sentence about data integration
https://doi.org/10.1073/pnas.2018093118

@@

NOT FULLY HAPPY with it
